Output Summary

### 2020-09-25 03-post-process/output-plots.Rmd
Add plots showing density-dependent relationship

>>>>

# Overwinter Survival Relationships

```{r overwinter-survival, fig.width = 4, fig.height = 7}

# extract parr, scale it to PEU, and add to posterior samples
Pa = post_subset(post, "^Pa[", matrix = T)
Pa_scaled = Pa/jags_data$peu
colnames(Pa_scaled) = gsub("Pa", "Pa_scaled", x = colnames(Pa_scaled))
post = post_bind(post, Pa_scaled)

# summarize posterior of scaled parr
Pa_scaled_mean = array_format(post_summ(post, "Pa_scaled")["mean",])
Pa_scaled_lwr = array_format(post_summ(post, "Pa_scaled")["2.5%",])
Pa_scaled_upr = array_format(post_summ(post, "Pa_scaled")["97.5%",])

# create vectors to predict survival at: for credible regions and mean curve
Pa_scaled_seq = matrix(NA, 30, 2)
Pa_scaled_seq[,1] = seq(min(Pa_scaled_lwr[,1], na.rm = T), max(Pa_scaled_upr[,1], na.rm = T), length = 30)
Pa_scaled_seq[,2] = seq(min(Pa_scaled_lwr[,2], na.rm = T), max(Pa_scaled_upr[,2], na.rm = T), length = 30)

# extract posteriors of coefficients
gamma0 = post_subset(post, "gamma0", matrix = T)
gamma1 = post_subset(post, "gamma1", matrix = T)

# extract/format posterior summaries of realized survivals
phi_Pa_Mb_mean = array_format(post_summ(post, "^phi_Pa_Mb[")["mean",])
phi_Pa_Mb_lwr = array_format(post_summ(post, "^phi_Pa_Mb[")["2.5%",])
phi_Pa_Mb_upr = array_format(post_summ(post, "^phi_Pa_Mb[")["97.5%",])

# function to create predicted survival curves for one posterior sample
f = function(i) {
  pred_phi_Pa_Mb1 = plogis(gamma0[i,1] + gamma1[i,1] * Pa_scaled_seq[,1])
  pred_phi_Pa_Mb2 = plogis(gamma0[i,2] + gamma1[i,2] * Pa_scaled_seq[,2])

  names(pred_phi_Pa_Mb1) = paste0("pred_phi_Pa_Mb[", 1:30, ",1]")
  names(pred_phi_Pa_Mb2) = paste0("pred_phi_Pa_Mb[", 1:30, ",2]")

  c(pred_phi_Pa_Mb1, pred_phi_Pa_Mb2)
}

# calculate predicted survivals and add to posterior samples
pred_phi_Pa_Mb = t(sapply(1:post_dim(post, "saved"), f))
post = post_bind(post, pred_phi_Pa_Mb)

# summarize predicted survivals
pred_phi_Pa_Mb_mean = array_format(post_summ(post, "pred_phi_Pa_Mb")["mean",])
pred_phi_Pa_Mb_lwr = array_format(post_summ(post, "pred_phi_Pa_Mb")["2.5%",])
pred_phi_Pa_Mb_upr = array_format(post_summ(post, "pred_phi_Pa_Mb")["97.5%",])

# function to draw plot for one LH-type
plot_fun = function(i) {
  # blank plot of correct dimensions
  plot(1,1, type = "n", 
       ylim = range(pred_phi_Pa_Mb_lwr[,i], pred_phi_Pa_Mb_upr[,i], phi_Pa_Mb_lwr[,i], phi_Pa_Mb_upr[,i], na.rm = T),
       xlim = range(0, Pa_scaled_seq), 
       main = c("Fall Migrants", "Spring Migrants")[i]
  )

  # expected relationship
  polygon(c(Pa_scaled_seq[,i], rev(Pa_scaled_seq[,i])), c(pred_phi_Pa_Mb_lwr[,i], rev(pred_phi_Pa_Mb_upr[,i])), border = NA, col = alpha("salmon", 0.5))
  lines(pred_phi_Pa_Mb_lwr[,i] ~ Pa_scaled_seq[,i], col = "red", lty = 2)
  lines(pred_phi_Pa_Mb_upr[,i] ~ Pa_scaled_seq[,i], col = "red", lty = 2)
  lines(pred_phi_Pa_Mb_mean[,i] ~ Pa_scaled_seq[,i], col = "red", lwd = 2)

  # realized survivals
  segments(Pa_scaled_lwr[,i], phi_Pa_Mb_mean[,i], Pa_scaled_upr[,i], phi_Pa_Mb_mean[,i], col = alpha("red", 0.5))
  segments(Pa_scaled_mean[,i], phi_Pa_Mb_lwr[,i], Pa_scaled_mean[,i], phi_Pa_Mb_upr[,i], col = alpha("red", 0.5))
  points(phi_Pa_Mb_mean[,i] ~ Pa_scaled_mean[,i], pch = 21, col = "red", bg = alpha("salmon", 0.5))
}

# create the plot
par(mfrow = c(2,1), mgp = c(2,0.35, 0), tcl = -0.15, mar = c(1,1,2,1), oma = c(2,2,0,0))
plot_fun(1)
plot_fun(2)
mtext(side = 1, line = 1, outer = T, "LH-Specific Parr/PEU", cex = 1.2)
mtext(side = 2, line = 1, outer = T, "Overwinter Survival", cex = 1.2)
```
